\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2018-11-22 fully-abstract-comp/popl2019/paper.tex
Fix title (second try).

%% Title information
\title[\stktokens{}: Enforcing WBCF and LSE using linear capabilities]{\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities}
% \titlenote{with title note}
% \subtitle{Fully abstract overlay semantics}
% \subtitlenote{with subtitle note}

>>>>

%% Title information
\title[\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using \ldots]{\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities}
% \titlenote{with title note}
% \subtitle{Fully abstract overlay semantics}
% \subtitlenote{with subtitle note}
